# Results Simulation Study

The code to obtain the figures and tables of "Supporting Information 3" can be found in this R-code.

First, we need to define the following variables:

-   `ro`: the $\rho$ values defined to obtain different cancer lethality levels in Scenario 0, Scenario 1 and Scenario 2 of the simulation study.

-   `var_error`: the standard deviation values defined for the unstructured spatial effects defined in Scenario 1, Scenario 2 and Scenario 4 of the simulation study..

-   `n.sim`: number of simulations.

-   `n`: number of areas.

-   `scenarios`: name of the scenarios defined in the simulation study.

-   `known.per`: percentages of coverage defined.

-   `missing.areas`: a list with the index of the areas that are going to be considered as missing

-   `selec.model`: a vector with the name of the shared component model selected for each scenario. The model options are M1, M2 and M3.

-   `selec.name`: a vector with the type of the shared component model selected for each scenario. For M1 we use *unst*, for M2 *unst2* and for M 3 *unst2_indep*.

-   `selec.prior`: the spatial priors selected for the M-models for each scenario.

-   `selec.method`: the modeling method selected for the M-models for each scenario.

```{r}
rm(list=ls())

## Necessary constant
ro <- c(0.3,0.5,0.7,0.9)
var_error <- c(0.2)

n.sim <- 80
n <- 47

scenarios <- c("S1","S2", "S3","S4")
known.per <- c("90","80","70","60","50","40","30")

missing.areas <- list(
  c(05,08,33,37,44),
  c(05,08,23,33,35,37,39,44,46),
  c(05,08,14,23,26,31,33,34,35,36,37,39,44,46),
  c(05,06,08,09,14,18,23,26,31,33,34,35,36,37,39,44,46),
  c(04,05,06,08,09,10,13,14,18,20,22,23,26,28,31,33,34,35,36,37,38,39,44,46),
  c(03,04,05,06,08,09,10,13,14,18,20,22,23,26,27,28,31,33,34,35,36,37,38,39,
    41,42,43,44,46),
  c(03,04,05,06,07,08,09,10,13,14,18,20,21,22,23,24,26,27,28,31,33,34,35,36,
    37,38,39,41,42,43,44,46)
)

selec.model <- c("M1","M2","M1","M2")
selec.name <- c("unst","unst2","unst","unst2")

selec.prior <- c("BYM2","BYM2","BYM2","BYM2")
selec.method <- c("FE","RE","FE","RE")

```

## Table 1 and table 2

In this section you will find the code to obtain the tables of the Supporting Information 3.

```{r}
MARB_tab <- matrix(NA, ncol=length(known.per),
                   nrow=length(ro)*4+4+length(scenarios)+3)
DSS_tab <- matrix(NA, ncol=length(known.per),
                   nrow=length(ro)*4+4+length(scenarios)+3)


for (s in 1:length(scenarios)) {
  if (scenarios[s]=="S3") {
    #Simulated data
    eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/SimulationStudy_",scenarios[s],".Rdata')")))
  
    population <- DataSIM$population[which(DataSIM$sim==1)]
    count <- exp(logRate)*population
    
    for (kp in 1:length(known.per)) {
      result_SCM<-list()
      result_M_model<-list()
      
      #Estimated results
      ##SCM
      eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/",selec.model[s],"/",scenarios[s],"_",selec.model[s],".Rdata')")))
      eval(parse(text = paste0("result_SCM <- results_shared_",selec.name[s])))
  
      ##M Model
      eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/",scenarios[s],"_",selec.prior[s],"_",selec.method[s],".Rdata')")))
      eval(parse(text = paste0("result_M_Model <- results_",selec.prior[s],"_",selec.method[s],"_specI")))

      #MARB
      MARB_SCM_i <- Reduce(`+`,lapply(1:n.sim, function(x) abs(result_SCM[[x]]$summary.fitted.values[,1]-exp(logRate))/exp(logRate)))/n.sim
        
      MARB_tab[4*length(ro)+6,kp] <- round(mean(MARB_SCM_i[missing.areas[[kp]]]),3)
      
      MARB_M_Model_i <- Reduce(`+`,lapply(1:n.sim, function(x) abs(result_M_Model[[x]]$summary.fitted.values[,1]-exp(logRate))/exp(logRate)))/n.sim

      MARB_tab[4*length(ro)+7,kp] <- round(mean(MARB_M_Model_i[missing.areas[[kp]]]),3)
        
      #DSS
      sd_C_SCM <- lapply(1:n.sim, function(x) sqrt(population*result_SCM[[x]]$summary.fitted.values[,1]+population^2*(result_SCM[[x]]$summary.fitted.values[,2]^2)))
      mean_C_SCM <- lapply(1:n.sim, function(x) population*result_SCM[[x]]$summary.fitted.values[,1])
        
      DSS_SCM_i <- Reduce(`+`,lapply(1:n.sim, function(x) ((count-mean_C_SCM[[x]])/sd_C_SCM[[x]])^2+2*log(sd_C_SCM[[x]])))/n.sim
        
      DSS_tab[4*length(ro)+6,kp] <- round(mean(DSS_SCM_i[missing.areas[[kp]]]),3)
      
      sd_C_M_Model <- lapply(1:n.sim, function(x) sqrt(population*result_M_Model[[x]]$summary.fitted.values[,1]+population^2*(result_M_Model[[x]]$summary.fitted.values[,2]^2)))
      mean_C_M_Model <- lapply(1:n.sim, function(x) population*result_M_Model[[x]]$summary.fitted.values[,1])

      DSS_M_Model_i <- Reduce(`+`,lapply(1:n.sim, function(x) ((count-mean_C_M_Model[[x]])/sd_C_M_Model[[x]])^2+2*log(sd_C_M_Model[[x]])))/n.sim

      DSS_tab[4*length(ro)+7,kp] <- round(mean(DSS_M_Model_i[missing.areas[[kp]]]),3)
        
    }
  }
  else{
    for (v in 1:length(var_error)) {
      if (scenarios[s]=="S1") {
        for (r in 1:length(ro)) {
          #Simulated data
          eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/SimulationStudy_",scenarios[s],"_ro_",ro[r],"_sd_error_",var_error[v],".Rdata')")))
          population <- DataSIM$population[which(DataSIM$sim==1)]
          count <- exp(logRate)*population
          
          for (kp in 1:length(known.per)) {
            result_SCM<-list()
            result_M_model<-list()
      
            #Estimated results
            ##SCM
            eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/",selec.model[s],"/ro_",ro[r],"_sd_",var_error[v],"/",scenarios[s],"_",selec.model[s],"_ro_",ro[r],"_sd_",var_error[v],".Rdata')")))
            eval(parse(text = paste0("result_SCM <- results_shared_",selec.name[s])))
  
            ##M Model
            eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/ro_",ro[r],"_sd_",var_error[v],"/",scenarios[s],"_",selec.prior[s],"_",selec.method[s],"_ro_",ro[r],"_sd_",var_error[v],".Rdata')")))
            eval(parse(text = paste0("result_M_Model <- results_",selec.prior[s],"_",selec.method[s],"_specI")))
      
            #MARB
            MARB_SCM_i <- Reduce(`+`,lapply(1:n.sim, function(x) abs(result_SCM[[x]]$summary.fitted.values[,1]-exp(logRate))/exp(logRate)))/n.sim
        
            MARB_tab[r+1,kp] <- round(mean(MARB_SCM_i[missing.areas[[kp]]]),3)
      
            MARB_M_Model_i <- Reduce(`+`,lapply(1:n.sim, function(x) abs(result_M_Model[[x]]$summary.fitted.values[,1]-exp(logRate))/exp(logRate)))/n.sim

            MARB_tab[r+2+length(ro),kp] <- round(mean(MARB_M_Model_i[missing.areas[[kp]]]),3)

            #DSS
            sd_C_SCM <- lapply(1:n.sim, function(x) sqrt(population*result_SCM[[x]]$summary.fitted.values[,1]+population^2*(result_SCM[[x]]$summary.fitted.values[,2]^2)))
            mean_C_SCM <- lapply(1:n.sim, function(x) population*result_SCM[[x]]$summary.fitted.values[,1])
        
            DSS_SCM_i <- Reduce(`+`,lapply(1:n.sim, function(x) ((count-mean_C_SCM[[x]])/sd_C_SCM[[x]])^2+2*log(sd_C_SCM[[x]])))/n.sim
        
            DSS_tab[r+1,kp] <- round(mean(DSS_SCM_i[missing.areas[[kp]]]),3)
      
            sd_C_M_Model <- lapply(1:n.sim, function(x) sqrt(population*result_M_Model[[x]]$summary.fitted.values[,1]+population^2*(result_M_Model[[x]]$summary.fitted.values[,2]^2)))
            mean_C_M_Model <- lapply(1:n.sim, function(x) population*result_M_Model[[x]]$summary.fitted.values[,1])

            DSS_M_Model_i <- Reduce(`+`,lapply(1:n.sim, function(x) ((count-mean_C_M_Model[[x]])/sd_C_M_Model[[x]])^2+2*log(sd_C_M_Model[[x]])))/n.sim

            DSS_tab[r+2+length(ro),kp] <- round(mean(DSS_M_Model_i[missing.areas[[kp]]]),3)

          }
        }
      }
      if (scenarios[s]=="S2") {
        for (r in 1:length(ro)) {
          #Simulated data
          eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/SimulationStudy_",scenarios[s],"_ro_",ro[r],"_sd_error_",var_error[v],".Rdata')")))
          population <- DataSIM$population[which(DataSIM$sim==1)]
          count <- exp(logRate)*population

          for (kp in 1:length(known.per)) {
            result_SCM<-list()
            result_M_model<-list()

            #Estimated results
            ##SCM
            eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/",selec.model[s],"/ro_",ro[r],"_sd_",var_error[v],"/",scenarios[s],"_",selec.model[s],"_ro_",ro[r],"_sd_",var_error[v],".Rdata')")))
            eval(parse(text = paste0("result_SCM <- results_shared_",selec.name[s])))

            ##M Model
            eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/ro_",ro[r],"_sd_",var_error[v],"/",scenarios[s],"_",selec.prior[s],"_",selec.method[s],"_ro_",ro[r],"_sd_",var_error[v],".Rdata')")))
            eval(parse(text = paste0("result_M_Model <- results_",selec.prior[s],"_",selec.method[s],"_specI")))

            #MARB
            MARB_SCM_i <- Reduce(`+`,lapply(1:n.sim, function(x) abs(result_SCM[[x]]$summary.fitted.values[,1]-exp(logRate))/exp(logRate)))/n.sim

            MARB_tab[r+3+2*length(ro),kp] <- round(mean(MARB_SCM_i[missing.areas[[kp]]]),3)

            MARB_M_Model_i <- Reduce(`+`,lapply(1:n.sim, function(x) abs(result_M_Model[[x]]$summary.fitted.values[,1]-exp(logRate))/exp(logRate)))/n.sim

            MARB_tab[r+4+3*length(ro),kp] <- round(mean(MARB_M_Model_i[missing.areas[[kp]]]),3)

            #DSS
            sd_C_SCM <- lapply(1:n.sim, function(x) sqrt(population*result_SCM[[x]]$summary.fitted.values[,1]+population^2*(result_SCM[[x]]$summary.fitted.values[,2]^2)))
            mean_C_SCM <- lapply(1:n.sim, function(x) population*result_SCM[[x]]$summary.fitted.values[,1])

            DSS_SCM_i <- Reduce(`+`,lapply(1:n.sim, function(x) ((count-mean_C_SCM[[x]])/sd_C_SCM[[x]])^2+2*log(sd_C_SCM[[x]])))/n.sim

            DSS_tab[r+3+2*length(ro),kp] <- round(mean(DSS_SCM_i[missing.areas[[kp]]]),3)

            sd_C_M_Model <- lapply(1:n.sim, function(x) sqrt(population*result_M_Model[[x]]$summary.fitted.values[,1]+population^2*(result_M_Model[[x]]$summary.fitted.values[,2]^2)))
            mean_C_M_Model <- lapply(1:n.sim, function(x) population*result_M_Model[[x]]$summary.fitted.values[,1])

            DSS_M_Model_i <- Reduce(`+`,lapply(1:n.sim, function(x) ((count-mean_C_M_Model[[x]])/sd_C_M_Model[[x]])^2+2*log(sd_C_M_Model[[x]])))/n.sim

            DSS_tab[r+4+3*length(ro),kp] <- round(mean(DSS_M_Model_i[missing.areas[[kp]]]),3)

          }
        }
      }
      if (scenarios[s]=="S4") {
        #Simulated data
        eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/SimulationStudy_",scenarios[s],"_sd_error_",var_error[v],".Rdata')")))
        
        population <- DataSIM$population[which(DataSIM$sim==1)]
        count <- exp(logRate)*population
          
        for (kp in 1:length(known.per)) {
          result_SCM<-list()
          result_M_model<-list()
      
          #Estimated results
          ##SCM
          eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/",selec.model[s],"/sd_",var_error[v],"/",scenarios[s],"_",selec.model[s],"_sd_",var_error[v],".Rdata')")))
          eval(parse(text = paste0("result_SCM <- results_shared_",selec.name[s])))
  
          ##M Model
          eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/sd_",var_error[v],"/",scenarios[s],"_",selec.prior[s],"_",selec.method[s],"_sd_",var_error[v],".Rdata')")))
          eval(parse(text = paste0("result_M_Model <- results_",selec.prior[s],"_",selec.method[s],"_specI")))

          #MARB
          MARB_SCM_i <- Reduce(`+`,lapply(1:n.sim, function(x) abs(result_SCM[[x]]$summary.fitted.values[,1]-exp(logRate))/exp(logRate)))/n.sim
        
          MARB_tab[4*length(ro)+10,kp] <- round(mean(MARB_SCM_i[missing.areas[[kp]]]),3)
      
          MARB_M_Model_i <- Reduce(`+`,lapply(1:n.sim, function(x) abs(result_M_Model[[x]]$summary.fitted.values[,1]-exp(logRate))/exp(logRate)))/n.sim

          MARB_tab[4*length(ro)+11,kp] <- round(mean(MARB_M_Model_i[missing.areas[[kp]]]),3)
        
          #DSS
          sd_C_SCM <- lapply(1:n.sim, function(x) sqrt(population*result_SCM[[x]]$summary.fitted.values[,1]+population^2*(result_SCM[[x]]$summary.fitted.values[,2]^2)))
          mean_C_SCM <- lapply(1:n.sim, function(x) population*result_SCM[[x]]$summary.fitted.values[,1])
        
          DSS_SCM_i <- Reduce(`+`,lapply(1:n.sim, function(x) ((count-mean_C_SCM[[x]])/sd_C_SCM[[x]])^2+2*log(sd_C_SCM[[x]])))/n.sim
        
          DSS_tab[4*length(ro)+10,kp] <- round(mean(DSS_SCM_i[missing.areas[[kp]]]),3)
      
          sd_C_M_Model <- lapply(1:n.sim, function(x) sqrt(population*result_M_Model[[x]]$summary.fitted.values[,1]+population^2*(result_M_Model[[x]]$summary.fitted.values[,2]^2)))
          mean_C_M_Model <- lapply(1:n.sim, function(x) population*result_M_Model[[x]]$summary.fitted.values[,1])

          DSS_M_Model_i <- Reduce(`+`,lapply(1:n.sim, function(x) ((count-mean_C_M_Model[[x]])/sd_C_M_Model[[x]])^2+2*log(sd_C_M_Model[[x]])))/n.sim

          DSS_tab[4*length(ro)+11,kp] <- round(mean(DSS_M_Model_i[missing.areas[[kp]]]),3)
        
        }
      }
    }
  }
}

criterias <- c("MARB","DSS")
## Table for latex
for (c in 1:length(criterias)) {
  eval(parse(text = paste0(criterias[c],"_tab <- cbind(
  c('Scenario1','",selec.model[1],"',rep(' ',length(ro)),'M4',rep(' ',length(ro)),'Scenario2','",selec.model[2],"',rep(' ',length(ro)),'M4',rep(' ',length(ro)),'Scenario3','",selec.model[3],"','M4',' ','Scenario4','",selec.model[4],"','M4'),
  c(' ','SCM',rep(' ',length(ro)),paste('",selec.prior[1]," ",selec.method[1],"'),rep(' ',length(ro)),' ','SCM',rep(' ',length(ro)),paste('",selec.prior[2]," ",selec.method[2],"'),rep(' ',length(ro)),' ','SCM',paste('",selec.prior[3]," ",selec.method[3],"'),' ',' ','SCM',paste('",selec.prior[4]," ",selec.method[4],"')),
  c(' ',ro,' ',ro,' ',ro,' ',ro,rep(' ',7)),
               ",criterias[c],"_tab)")))
    
    eval(parse(text = paste0(criterias[c],"_tab <- rbind(
    c('",criterias[c],"',rep(' ',9)),
    c(' ',' ','ro',known.per),
                             ",criterias[c],"_tab)")))
    
    eval(parse(text = paste0("latex_table <- xtable::xtable(",criterias[c],"_tab, caption='Model selection ",criterias[c],"', digits=3)")))
    xtable::print.xtable(latex_table, include.rownames = FALSE,include.colnames = FALSE, comment=FALSE, caption.placement = getOption("xtable.caption.placement", "top"))
    
}



```

## Figure 1

In this section you will find the code to obtain the figure of the Supporting Information 3.

```{r}
library(ggplot2)

for (s in 1:length(scenarios)) {
  if (scenarios[s]=="S3") {
    #Simulated data
    eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/SimulationStudy_",scenarios[s],".Rdata')")))
  
    population <- DataSIM$population[which(DataSIM$sim==1)]
    count <- exp(logRate)*population
    
    for (kp in 1:length(known.per)) {
      SCM <- data.frame()
      M_Model <- data.frame()
      result_SCM<-list()
      result_M_model<-list()
      
      #Estimated results
      ##SCM
      eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/",selec.model[s],"/",scenarios[s],"_",selec.model[s],".Rdata')")))
      eval(parse(text = paste0("result_SCM <- results_shared_",selec.name[s])))
  
      ##M Model
      eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/",scenarios[s],"_",selec.prior[s],"_",selec.method[s],".Rdata')")))
      eval(parse(text = paste0("result_M_Model <- results_",selec.prior[s],"_",selec.method[s],"_specI")))

      rates.j_SCM <- t(sapply(1:n.sim, function(x) result_SCM[[x]]$summary.fitted.values[,1]*10^5))
      rates.j_M_Model <- t(sapply(1:n.sim, function(x) result_M_Model[[x]]$summary.fitted.values[,1]*10^5))
      
      eval(parse(text = paste0("data_frame_SCM <- cbind(rep(",known.per[kp],",n.sim),rates.j_SCM)")))
      SCM <- rbind(SCM,data_frame_SCM)
      
      eval(parse(text = paste0("data_frame_M_Model <- cbind(rep(",known.per[kp],",n.sim),rates.j_M_Model)")))
      M_Model <- rbind(M_Model,data_frame_M_Model)
      
      
      reg_index <- n*2
      colnames(SCM) <- c("percentage",paste0("P",1:reg_index))
      colnames(M_Model) <- c("percentage",paste0("P",1:reg_index))
      Data <- cbind(rep(c("SCM","MM"),each=dim(SCM)[1]),rbind(SCM,M_Model))
      colnames(Data)[1] <- "Model"
      Data$percentage <- as.factor(Data$percentage)
          

      pdf(file=paste0("./figures/Boxplot/Boxplot_",scenarios[s],"_",known.per[kp],".pdf"),height=10, width=12)
      for (l in missing.areas[[kp]]) {
        eval(parse(text = paste0("means <- aggregate(P",l," ~ Model + percentage, Data, mean)")))
        real <- means
        real[,3] <- rep(exp(logRate[l])*10^5,2*length(known.per[[kp]]))
            
        eval(parse(text = paste0("p <-ggplot(Data,aes(x=percentage, y=P",l,", color = Model))")))
        p <- p +
        geom_boxplot(outlier.shape=16,
                     outlier.size=6,  size=3) +
        theme(legend.position="top") +
        scale_x_discrete(name = "Percentage of Missing data") 
        eval(parse(text = paste0("p <- p +
                                 scale_y_continuous(name = 'rate values per 10^5 habitants',
                                 breaks = seq(ceiling(min(Data$P",l,",real$P",l,")), floor(max(Data$P",l,",real$P",l,")), by = 5))")))
  
        p <- p +
          ggtitle(paste0("Province ",l)) +
          theme(axis.text.x=element_blank(), axis.ticks.x = element_blank(),
                axis.title.x = element_blank(), text = element_text(size = 40),
                axis.text.y=element_text(size = rel(1.2)),
                plot.title = element_text (hjust = 0.5 ),
                panel.grid.minor = element_blank()) 
                              
        eval(parse(text = paste0("p <- p + geom_point(data = means, aes(y = P",l,", x = percentage),position=position_dodge2(width=.75), fill = 'black', size =5)  +
        geom_point(data = real, aes(y = P",l,", x = percentage),position=position_dodge2(width=.75), color = 'black', size =8)")))

        print(p)
            
      }
      dev.off()
      
    }
  }
  else{
    for (v in 1:length(var_error)) {
      if (scenarios[s]=="S1") {
        for (r in 1:length(ro)) {
          #Simulated data
          eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/SimulationStudy_",scenarios[s],"_ro_",ro[r],"_sd_error_",var_error[v],".Rdata')")))
          population <- DataSIM$population[which(DataSIM$sim==1)]
          count <- exp(logRate)*population

          for (kp in 1:length(known.per)) {
            SCM <- data.frame()
            M_Model <- data.frame()
            result_SCM<-list()
            result_M_model<-list()
            
            #Estimated results
            ##SCM
            eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/",selec.model[s],"/ro_",ro[r],"_sd_",var_error[v],"/",scenarios[s],"_",selec.model[s],"_ro_",ro[r],"_sd_",var_error[v],".Rdata')")))
            eval(parse(text = paste0("result_SCM <- results_shared_",selec.name[s])))

            ##M Model
            eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/ro_",ro[r],"_sd_",var_error[v],"/",scenarios[s],"_",selec.prior[s],"_",selec.method[s],"_ro_",ro[r],"_sd_",var_error[v],".Rdata')")))
            eval(parse(text = paste0("result_M_Model <- results_",selec.prior[s],"_",selec.method[s],"_specI")))
            
            rates.j_SCM <- t(sapply(1:n.sim, function(x) result_SCM[[x]]$summary.fitted.values[,1]*10^5))
            rates.j_M_Model <- t(sapply(1:n.sim, function(x) result_M_Model[[x]]$summary.fitted.values[,1]*10^5))
      
            eval(parse(text = paste0("data_frame_SCM <- cbind(rep(",known.per[kp],",n.sim),rates.j_SCM)")))
            SCM <- rbind(SCM,data_frame_SCM)
      
            eval(parse(text = paste0("data_frame_M_Model <- cbind(rep(",known.per[kp],",n.sim),rates.j_M_Model)")))
            M_Model <- rbind(M_Model,data_frame_M_Model)
      
      
            reg_index <- n*2
            colnames(SCM) <- c("percentage",paste0("P",1:reg_index))
            colnames(M_Model) <- c("percentage",paste0("P",1:reg_index))
            Data <- cbind(rep(c("SCM","MM"),each=dim(SCM)[1]),rbind(SCM,M_Model))
            colnames(Data)[1] <- "Model"
            Data$percentage <- as.factor(Data$percentage)
          

            pdf(file=paste0("./figures/Boxplot/Boxplot_",scenarios[s],"_ro_",ro[r],"_",known.per[kp],".pdf"),height=10, width=12)
            for (l in missing.areas[[kp]]) {
              eval(parse(text = paste0("means <- aggregate(P",l," ~ Model + percentage, Data, mean)")))
              real <- means
              real[,3] <- rep(exp(logRate[l])*10^5,2*length(known.per[[kp]]))
            
              eval(parse(text = paste0("p <-ggplot(Data,aes(x=percentage, y=P",l,", color = Model))")))
              p <- p +
              geom_boxplot(outlier.shape=16,
                          outlier.size=6,  size=3) +
              theme(legend.position="top") +
              scale_x_discrete(name = "Percentage of Missing data") 
              eval(parse(text = paste0("p <- p +
                                       scale_y_continuous(name = 'rate values per 10^5 habitants',
                                       breaks = seq(ceiling(min(Data$P",l,",real$P",l,")),
                                       floor(max(Data$P",l,",real$P",l,")), by = 5))")))
  
              p <- p +
                ggtitle(paste0("Province ",l)) +
                theme(axis.text.x=element_blank(), axis.ticks.x = element_blank(),
                      axis.title.x = element_blank(), text = element_text(size = 40),
                      axis.text.y=element_text(size = rel(1.2)),
                      plot.title = element_text (hjust = 0.5 ),
                      panel.grid.minor = element_blank()) 
                              
              eval(parse(text = paste0("p <- p + geom_point(data = means, aes(y = P",l,", x = percentage),position=position_dodge2(width=.75), fill = 'black', size =5)  +
        geom_point(data = real, aes(y = P",l,", x = percentage),position=position_dodge2(width=.75), color = 'black', size =8)")))

              print(p)
            
            }
            dev.off()
          }
        }
      }
      if (scenarios[s]=="S2") {
        for (r in 1:length(ro)) {
          #Simulated data
          eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/SimulationStudy_",scenarios[s],"_ro_",ro[r],"_sd_error_",var_error[v],".Rdata')")))
          population <- DataSIM$population[which(DataSIM$sim==1)]
          count <- exp(logRate)*population

          for (kp in 1:length(known.per)) {
            SCM <- data.frame()
            M_Model <- data.frame()
            result_SCM <- list()
            result_M_model <- list()

            #Estimated results
            ##SCM
            eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/",selec.model[s],"/ro_",ro[r],"_sd_",var_error[v],"/",scenarios[s],"_",selec.model[s],"_ro_",ro[r],"_sd_",var_error[v],".Rdata')")))
            eval(parse(text = paste0("result_SCM <- results_shared_",selec.name[s])))

            ##M Model
            eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/ro_",ro[r],"_sd_",var_error[v],"/",scenarios[s],"_",selec.prior[s],"_",selec.method[s],"_ro_",ro[r],"_sd_",var_error[v],".Rdata')")))
            eval(parse(text = paste0("result_M_Model <- results_",selec.prior[s],"_",selec.method[s],"_specI")))
            
            rates.j_SCM <- t(sapply(1:n.sim, function(x) result_SCM[[x]]$summary.fitted.values[,1]*10^5))
            rates.j_M_Model <- t(sapply(1:n.sim, function(x) result_M_Model[[x]]$summary.fitted.values[,1]*10^5))
      
            eval(parse(text = paste0("data_frame_SCM <- cbind(rep(",known.per[kp],",n.sim),rates.j_SCM)")))
            SCM <- rbind(SCM,data_frame_SCM)
      
            eval(parse(text = paste0("data_frame_M_Model <- cbind(rep(",known.per[kp],",n.sim),rates.j_M_Model)")))
            M_Model <- rbind(M_Model,data_frame_M_Model)
      
      
            reg_index <- n*2
            colnames(SCM) <- c("percentage",paste0("P",1:reg_index))
            colnames(M_Model) <- c("percentage",paste0("P",1:reg_index))
            Data <- cbind(rep(c("SCM","MM"),each=dim(SCM)[1]),rbind(SCM,M_Model))
            colnames(Data)[1] <- "Model"
            Data$percentage <- as.factor(Data$percentage)
          

            pdf(file=paste0("./figures/Boxplot/Boxplot_",scenarios[s],"_ro_",ro[r],"_",known.per[kp],".pdf"),height=10, width=12)
            for (l in missing.areas[[kp]]) {
              eval(parse(text = paste0("means <- aggregate(P",l," ~ Model + percentage, Data, mean)")))
              real <- means
              real[,3] <- rep(exp(logRate[l])*10^5,2*length(known.per[[kp]]))
            
              eval(parse(text = paste0("p <-ggplot(Data,aes(x=percentage, y=P",l,", color = Model))")))
              p <- p +
              geom_boxplot(outlier.shape=16,
                          outlier.size=6,  size=3) +
              theme(legend.position="top") +
              scale_x_discrete(name = "Percentage of Missing data") 
              eval(parse(text = paste0("p <- p +
                                       scale_y_continuous(name = 'rate values per 10^5 habitants',
                                       breaks = seq(ceiling(min(Data$P",l,",real$P",l,")),
                                       floor(max(Data$P",l,",real$P",l,")), by = 5))")))
  
              p <- p +
                ggtitle(paste0("Province ",l)) +
                theme(axis.text.x=element_blank(), axis.ticks.x = element_blank(),
                      axis.title.x = element_blank(), text = element_text(size = 40),
                      axis.text.y=element_text(size = rel(1.2)),
                      plot.title = element_text (hjust = 0.5 ),
                      panel.grid.minor = element_blank()) 
                              
              eval(parse(text = paste0("p <- p + geom_point(data = means, aes(y = P",l,", x = percentage),position=position_dodge2(width=.75), fill = 'black', size =5)  +
        geom_point(data = real, aes(y = P",l,", x = percentage),position=position_dodge2(width=.75), color = 'black', size =8)")))

              print(p)
            
            }
            dev.off()
          }
        }
      }
      if (scenarios[s]=="S4") {
        #Simulated data
        eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/SimulationStudy_",scenarios[s],"_sd_error_",var_error[v],".Rdata')")))

        population <- DataSIM$population[which(DataSIM$sim==1)]
        count <- exp(logRate)*population

        for (kp in 1:length(known.per)) {
          SCM <- data.frame()
          M_Model <- data.frame()

          #Estimated results
          ##SCM
          eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/",selec.model[s],"/sd_",var_error[v],"/",scenarios[s],"_",selec.model[s],"_sd_",var_error[v],".Rdata')")))
          eval(parse(text = paste0("result_SCM <- results_shared_",selec.name[s])))

          ##M Model
          eval(parse(text= paste0("load('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/sd_",var_error[v],"/",scenarios[s],"_",selec.prior[s],"_",selec.method[s],"_sd_",var_error[v],".Rdata')")))
          eval(parse(text = paste0("result_M_Model <- results_",selec.prior[s],"_",selec.method[s],"_specI")))
          
          rates.j_SCM <- t(sapply(1:n.sim, function(x) result_SCM[[x]]$summary.fitted.values[,1]*10^5))
          rates.j_M_Model <- t(sapply(1:n.sim, function(x) result_M_Model[[x]]$summary.fitted.values[,1]*10^5))
      
          eval(parse(text = paste0("data_frame_SCM <- cbind(rep(",known.per[kp],",n.sim),rates.j_SCM)")))
          SCM <- rbind(SCM,data_frame_SCM)
      
          eval(parse(text = paste0("data_frame_M_Model <- cbind(rep(",known.per[kp],",n.sim),rates.j_M_Model)")))
          M_Model <- rbind(M_Model,data_frame_M_Model)
      
          reg_index <- n*2
          colnames(SCM) <- c("percentage",paste0("P",1:reg_index))
          colnames(M_Model) <- c("percentage",paste0("P",1:reg_index))
          Data <- cbind(rep(c("SCM","MM"),each=dim(SCM)[1]),rbind(SCM,M_Model))
          colnames(Data)[1] <- "Model"
          Data$percentage <- as.factor(Data$percentage)
          
          pdf(file=paste0("./figures/Boxplot/Boxplot_",scenarios[s],"_",known.per[kp],".pdf"),height=10, width=12)
          for (l in missing.areas[[kp]]) {
            eval(parse(text = paste0("means <- aggregate(P",l," ~ Model + percentage, Data, mean)")))
            real <- means
            real[,3] <- rep(exp(logRate[l])*10^5,2*length(known.per[[kp]]))
          
            eval(parse(text = paste0("p <-ggplot(Data,aes(x=percentage, y=P",l,", color = Model))")))
            p <- p +
            geom_boxplot(outlier.shape=16,
                        outlier.size=6,  size=3) +
            theme(legend.position="top") +
            scale_x_discrete(name = "Percentage of Missing data") 
            eval(parse(text = paste0("p <- p +
                                     scale_y_continuous(name = 'rate values per 10^5 habitants',
                                     breaks = seq(ceiling(min(Data$P",l,",real$P",l,")),
                                     floor(max(Data$P",l,",real$P",l,")), by = 5))")))
  
            p <- p +
              ggtitle(paste0("Province ",l)) +
              theme(axis.text.x=element_blank(), axis.ticks.x = element_blank(),
                    axis.title.x = element_blank(), text = element_text(size = 40),
                    axis.text.y=element_text(size = rel(1.2)),
                    plot.title = element_text (hjust = 0.5 ),
                    panel.grid.minor = element_blank()) 
                            
            eval(parse(text = paste0("p <- p + geom_point(data = means, aes(y = P",l,", x = percentage),position=position_dodge2(width=.75), fill = 'black', size =5)  +
        geom_point(data = real, aes(y = P",l,", x = percentage),position=position_dodge2(width=.75), color = 'black', size =8)")))

            print(p)
            
          }
          dev.off()
        }
      }
    }
  }
}
```
