# Select Simulations

As mentioned in previous codes, for each scenario 140 simulations have been performed, from which 100 simulations that have obtained convergence in the different coverage percentages defined will be selected. The code to select 100 simulations can be found in this R code.

First, we need to define the following variables:

-   `ro`: the $\rho$ values defined to obtain different cancer lethality levels in Scenario 0, Scenario 1 and Scenario 2 of the simulation study.

-   `var_error`: the standard deviation values defined for the unstructured spatial effects defined in Scenario 1, Scenario 2 and Scenario 4 of the simulation study.

-   `n`: number of areas.

-   `n.sim`: number of simulations.

-   `n.save`: the number used to save the results of the models. It must always start with 0. In this case, as we have saved the results of the simulation study 20 by 20, the numbers are 20, 40, 60, 80, 100, 120 and 140.

-   `model.type`: model name used for each shared component model defined, i.e M1, M2 and M3.

-   `name.model`: type of the shared component model defined. For M1 we use *unst*, for M2 *unst2* and for M 3 *unst2_indep*.

-   `priors`: the spatial priors defined for the M-models.

-   `method`: the modeling method used for the M-models.

-   `scenarios`: name of the scenarios defined in the simulation study.

-   `known.per`: percentages of coverage defined.

```{r}
## Necessary constant
ro<-c(0.3,0.5,0.7,0.9)
var_error <- c(0.05,0.1,0.2)

n <- 47
n.sim<-140
n.save<-seq(0,n.sim,by=20)

model.type <- c("M1","M2","M3")
name.model <- c("unst","unst2","unst2_indep")

priors <- c("iCAR","pCAR","LCAR","BYM","BYM2")
method <- c("FE","RE")

scenarios <- c("S0","S1","S2","S3","S4")
known.per <- c("100","90","80","70","60","50","40","30")

```

Once the required variables have been defined, we can select the 100 simulations. These simulations are different according to the scenario analysed. We save the selected simulations in the folder `Selected_Simulations`. Therefore, we need to create the folder `Selected_Simulations`. In this folder we will save only the 100 selected simulations for each scenario and a vector with the number of selected simulations.

```{r}
## Folder to save results
if(!file.exists('./Selected_Simulations'))
{dir.create('./Selected_Simulations')}

## Folder to save results
for (s in 1:length(scenarios)) {
  eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"'))
{dir.create('./Selected_Simulations/",scenarios[s],"')}")))
}

```

We select 100 simulations for each scenario.

```{r}
for (s in 1:length(scenarios)) {
  ###Scenario 0
  if (scenarios[s]=="S0"){
    selec_sim <- c(1:n.sim)
    for (kp in 1:length(known.per)){
      for (i in 1:length(ro)) {
        for (j in 2:length(n.save)) {
          ##Shared Component Model
          for (mt in 1:length(model.type)) {
          eval(parse(text = paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/SCM/",model.type[mt],"/ro_",ro[i],"/",scenarios[s],"_",model.type[mt],"_ro_",ro[i],"_",n.save[j],".RData')")))
            eval(parse(text = paste0("res <- results_shared_",name.model[mt]))) 
        
            for (l in 1:length(res)) {
              if (is.null(res[[l]])){
                if (length(which(selec_sim==(l+n.save[j-1])))!=0){
                  selec_sim <- selec_sim[-which(selec_sim==(l+n.save[j-1]))]
                }
              }
            }
          }
          rm(list=c("res"))
          
          ## M-model
          for (p in 1:length(priors)) {
            for (d in 1:length(method)) {
              eval(parse(text= paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/M_Model/ro_",ro[i],"/",scenarios[s],"_",priors[p],"_",method[d],"_ro_",ro[i],"_",n.save[j],".RData')")))
              eval(parse(text = paste0("res <- results_",priors[p],"_",method[d],"_specI")))

              for (l in 1:length(res)) {
                if (is.null(res[[l]])){
                  if (length(which(selec_sim==(l+n.save[j-1])))!=0){
                   selec_sim <- selec_sim[-which(selec_sim==(l+n.save[j-1]))]
                  }
                }
              }
               rm(list=c("res"))
            }
          }
        }
      }
    }
    
    #choose 100 simulations
    set.seed(230821)
    selec_sim <- sort(sample(selec_sim,100,replace = F))
    
    #Save selected 100 simulations
    for (i in 1:length(ro)) {
      eval(parse(text= paste0("load('./",scenarios[s],"/SimulationStudy_",scenarios[s],"_ro_",ro[i],".Rdata')")))
    
    Data <- NULL
    for (ss in selec_sim) {
      Data <- rbind(Data,DataSIM[which(DataSIM$sim==ss),])
    }
    Data$disease <- factor(Data$disease, labels = c("inc","mort"))
    Data$sim <- rep(1:100,each=n*2)
        
    DataSIM <- Data

    eval(parse(text = paste0("save(list=c('DataSIM','logRate'), file='./Selected_Simulations/",scenarios[s],"/SimulationStudy_",scenarios[s],"_ro_",ro[i],".Rdata')")))
    }
    
    #Save selec_sim vector
    eval(parse(text = paste0("save(selec_sim, file='./Selected_Simulations/",scenarios[s],"/Selec_sim_",scenarios[s],".Rdata')")))
  }
  
  ###Scenario 1 and Scenario 2
  if (scenarios[s]=="S1" | scenarios[s]=="S2"){
    selec_sim <- c(1:n.sim)
    for (kp in 1:length(known.per)){
      for (i in 1:length(ro)) {
        for (v in 1:length(var_error)) {
          for (j in 2:length(n.save)) {
            ##Shared Component Model
            for (mt in 1:length(model.type)) {
            eval(parse(text = paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/SCM/",model.type[mt],"/ro_",ro[i],"_sd_",var_error[v],"/",scenarios[s],"_",model.type[mt],"_ro_",ro[i],"_sd_",var_error[v],"_",n.save[j],".RData')")))
              eval(parse(text = paste0("res <- results_shared_",name.model[mt]))) 
          
              for (l in 1:length(res)) {
                if (is.null(res[[l]])){
                  if (length(which(selec_sim==(l+n.save[j-1])))!=0){
                    selec_sim <- selec_sim[-which(selec_sim==(l+n.save[j-1]))]
                  }
                }
              }
            }
            rm(list=c("res"))
            
            ## M-model
            for (p in 1:length(priors)) {
              for (d in 1:length(method)) {
                eval(parse(text= paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/M_Model/ro_",ro[i],"_sd_",var_error[v],"/",scenarios[s],"_",priors[p],"_",method[d],"_ro_",ro[i],"_sd_",var_error[v],"_",n.save[j],".RData')")))
                eval(parse(text = paste0("res <- results_",priors[p],"_",method[d],"_specI")))

                for (l in 1:length(res)) {
                  if (is.null(res[[l]])){
                    if (length(which(selec_sim==(l+n.save[j-1])))!=0){
                     selec_sim <- selec_sim[-which(selec_sim==(l+n.save[j-1]))]
                    }
                  }
                }
                 rm(list=c("res"))
              }
            }
          }
        }
      }
    }
    
    #choose 100 simulations
    set.seed(230821)
    selec_sim <- sort(sample(selec_sim,100,replace = F))
    
    #Save selected 100 simulations
    for (i in 1:length(ro)) {
      for (v in 1:length(var_error)) {
        eval(parse(text= paste0("load('./",scenarios[s],"/SimulationStudy_",scenarios[s],"_ro_",ro[i],"_sd_error_",var_error[v],".Rdata')")))
    
        Data <- NULL
        for (ss in selec_sim) {
          Data <- rbind(Data,DataSIM[which(DataSIM$sim==ss),])
        }
        Data$disease <- factor(Data$disease, labels = c("inc","mort"))
        Data$sim <- rep(1:100,each=n*2)
        
        DataSIM <- Data

        eval(parse(text = paste0("save(list=c('DataSIM','logRate'), file='./Selected_Simulations/",scenarios[s],"/SimulationStudy_",scenarios[s],"_ro_",ro[i],"_sd_error_",var_error[v],".Rdata')")))
      }
    }
    #Save selec_sim vector
    eval(parse(text = paste0("save(selec_sim, file='./Selected_Simulations/",scenarios[s],"/Selec_sim_",scenarios[s],".Rdata')")))
  }
  
  ###Scenario 3
  if (scenarios[s]=="S3"){
    selec_sim <- c(1:n.sim)
    for (kp in 1:length(known.per)){
      for (j in 2:length(n.save)) {
        ##Shared Component Model
        for (mt in 1:length(model.type)) {
          eval(parse(text = paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/SCM/",model.type[mt],"/",scenarios[s],"_",model.type[mt],"_",n.save[j],".RData')")))
          eval(parse(text = paste0("res <- results_shared_",name.model[mt]))) 
        
          for (l in 1:length(res)) {
            if (is.null(res[[l]])){
              if (length(which(selec_sim==(l+n.save[j-1])))!=0){
                selec_sim <- selec_sim[-which(selec_sim==(l+n.save[j-1]))]
              }
            }
          }
        }
        rm(list=c("res"))
          
        ## M-model
        for (p in 1:length(priors)) {
          for (d in 1:length(method)) {
            eval(parse(text= paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/M_Model/",scenarios[s],"_",priors[p],"_",method[d],"_",n.save[j],".RData')")))
            eval(parse(text = paste0("res <- results_",priors[p],"_",method[d],"_specI")))

            for (l in 1:length(res)) {
              if (is.null(res[[l]])){
                if (length(which(selec_sim==(l+n.save[j-1])))!=0){
                 selec_sim <- selec_sim[-which(selec_sim==(l+n.save[j-1]))]
                }
              }
            }
            rm(list=c("res"))
          }
        }
      }
    }
    #choose 100 simulations
    set.seed(230821)
    selec_sim <- sort(sample(selec_sim,100,replace = F))
    
    #Save selected 100 simulations
    eval(parse(text= paste0("load('./",scenarios[s],"/SimulationStudy_",scenarios[s],".Rdata')")))
    
    Data <- NULL
    for (ss in selec_sim) {
      Data <- rbind(Data,DataSIM[which(DataSIM$sim==ss),])
    }
    Data$disease <- factor(Data$disease, labels = c("inc","mort"))
    Data$sim <- rep(1:100,each=n*2)
    
    DataSIM <- Data
    
    eval(parse(text = paste0("save(list=c('DataSIM','logRate'), file='./Selected_Simulations/",scenarios[s],"/SimulationStudy_",scenarios[s],".Rdata')")))
    
    #Save selec_sim vector
    eval(parse(text = paste0("save(selec_sim, file='./Selected_Simulations/",scenarios[s],"/Selec_sim_",scenarios[s],".Rdata')")))
  }
  
  ###Scenario 4
  if (scenarios[s]=="S4"){
    selec_sim <- c(1:n.sim)
    for (kp in 1:length(known.per)){
      for (v in 1:length(var_error)) {
        for (j in 2:length(n.save)) {
          ##Shared Component Model
          for (mt in 1:length(model.type)) {
          eval(parse(text = paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/SCM/",model.type[mt],"/sd_",var_error[v],"/",scenarios[s],"_",model.type[mt],"_sd_",var_error[v],"_",n.save[j],".RData')")))
            eval(parse(text = paste0("res <- results_shared_",name.model[mt]))) 
        
            for (l in 1:length(res)) {
              if (is.null(res[[l]])){
                if (length(which(selec_sim==(l+n.save[j-1])))!=0){
                  selec_sim <- selec_sim[-which(selec_sim==(l+n.save[j-1]))]
                }
              }
            }
          }
          rm(list=c("res"))
          
          ## M-model
          for (p in 1:length(priors)) {
            for (d in 1:length(method)) {
              eval(parse(text= paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/M_Model/sd_",var_error[v],"/",scenarios[s],"_",priors[p],"_",method[d],"_sd_",var_error[v],"_",n.save[j],".RData')")))
              eval(parse(text = paste0("res <- results_",priors[p],"_",method[d],"_specI")))

              for (l in 1:length(res)) {
                if (is.null(res[[l]])){
                  if (length(which(selec_sim==(l+n.save[j-1])))!=0){
                   selec_sim <- selec_sim[-which(selec_sim==(l+n.save[j-1]))]
                  }
                }
              }
               rm(list=c("res"))
            }
          }
        }
      }
    }
    #choose 100 simulations
    set.seed(230821)
    selec_sim <- sort(sample(selec_sim,100,replace = F))
    
    #Save selected 100 simulations
    for (v in 1:length(var_error)) {
      eval(parse(text= paste0("load('./",scenarios[s],"/SimulationStudy_",scenarios[s],"_sd_error_",var_error[v],".Rdata')")))
    
      Data <- NULL
      for (ss in selec_sim) {
        Data <- rbind(Data,DataSIM[which(DataSIM$sim==ss),])
      }
      Data$disease <- factor(Data$disease, labels = c("inc","mort"))
      Data$sim <- rep(1:100,each=n*2)
      
      DataSIM <- Data
      
      eval(parse(text = paste0("save(list=c('DataSIM','logRate'), file='./Selected_Simulations/",scenarios[s],"/SimulationStudy_",scenarios[s],"_sd_error_",var_error[v],".Rdata')")))
    }
      
    #Save selec_sim vector
    eval(parse(text = paste0("save(selec_sim, file='./Selected_Simulations/",scenarios[s],"/Selec_sim_",scenarios[s],".Rdata')")))
  }
  
}

```

To save time and space when analysing the results of the simulation study, we made a copy of the fitted models by saving only the results of the 100 selected simulations and the elements we were interested in. In our case, these are the DIC and WAIC values, the summary of the fitted values and the marginals of the fitted values. We save the results of the fitted models in the folder `Selected_Simulations` . In this case, we save the results of the 100 fitted models in the same file. First, we create the necessary folders to save the results.

```{r}
## Folder to save results
for (s in 1:length(scenarios)) {
  for (kp in 1:length(known.per)) {
    eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"')}")))
  
    ###### Shared Component Models
    eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM')}")))
  
    eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M1'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M1')}")))
  
    eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M2'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M2')}")))
  
    eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M3'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M3')}")))
    
    ###### M-models
    eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model')}")))
    
    if (scenarios[s]=="S1" | scenarios[s]=="S2"){
      for (r in 1:length(ro)) {
        for (v in 1:length(var_error)) {
          eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M1/sd_",var_error[v],"'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M1/ro_",ro[r],"_sd_",var_error[v],"')}")))
  
          eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M2/sd_",var_error[v],"'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M2/ro_",ro[r],"_sd_",var_error[v],"')}")))
    
          eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M3/sd_",var_error[v],"'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M3/ro_",ro[r],"_sd_",var_error[v],"')}")))
        
          eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/sd_",var_error[v],"'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/ro_",ro[r],"_sd_",var_error[v],"')}")))
        }
      }
    }
    else if (scenarios[s]=="S4"){
      for (v in 1:length(var_error)) {
        eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M1/sd_",var_error[v],"'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M1/sd_",var_error[v],"')}")))
  
        eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M2/sd_",var_error[v],"'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M2/sd_",var_error[v],"')}")))
    
        eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M3/sd_",var_error[v],"'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/M3/sd_",var_error[v],"')}")))
        
        eval(parse(text = paste0("if(!file.exists('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/sd_",var_error[v],"'))
{dir.create('./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/sd_",var_error[v],"')}")))
      }
    }
  }
}
```

Now, we save the results of the shared component models obtained in the 100 selected simulations and the elements we are interested in.

```{r}
#############################################################################################                    Shared Component Models                    ##########
###################################################################################


for (s in 1:length(scenarios)) {
  ###Scenario0
  if (scenarios[s]=="S0"){
    #Open selec_sim
    eval(parse(text = paste0("load('./Selected_Simulations/",scenarios[s],"/Selec_sim_",scenarios[s],".Rdata')")))
    for (kp in 1:length(known.per)){
      for (i in 1:length(ro)) {
        for (mt in 1:length(model.type)) {
          eval(parse(text = paste0("result_shared_",name.model[mt],"<-list()")))
          for (j in 2:length(n.save)) {
            eval(parse(text = paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/SCM/",model.type[mt],"/ro_",ro[i],"/",scenarios[s],"_",model.type[mt],"_ro_",ro[i],"_",n.save[j],".RData')")))
            eval(parse(text = paste0("result_shared_",name.model[mt],"[(n.save[j-1]+1):n.save[j]] <- results_shared_",name.model[mt],"[1:20]"))) 
          }
          
          eval(parse(text = paste0("results_shared_",name.model[mt],"<-list()")))
          
          eval(parse(text = paste0("save_index <- which(names(result_shared_",name.model[mt],"[[1]])=='dic' |
          names(result_shared_",name.model[mt],"[[1]])=='waic' |
          names(result_shared_",name.model[mt],"[[1]])=='summary.fitted.values' |
          names(result_shared_",name.model[mt],"[[1]])=='marginals.fitted.values')")))
          
          eval(parse(text = paste0("results_shared_",name.model[mt]," <- lapply(1:n.sim, function(x) result_shared_",name.model[mt],"[[x]][save_index])")))
          
          eval(parse(text = paste0("results_shared_",name.model[mt]," <- results_shared_",name.model[mt],"[selec_sim]")))
          
          eval(parse(text = paste0("save(results_shared_",name.model[mt],", file='./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/",model.type[mt],"/ro_",ro[i],"_sd_error_",var_error[v],"/",scenarios[s],"_",model.type[mt],"_ro_",ro[i],".Rdata')")))
          
        }
      }
    }
  }
  
  ###Scenario1 and Scenario2
  if (scenarios[s]=="S1" | scenarios[s]=="S2"){
    #Open selec_sim
    eval(parse(text = paste0("load('./Selected_Simulations/",scenarios[s],"/Selec_sim_",scenarios[s],".Rdata')")))
    for (kp in 1:length(known.per)){
      for (i in 1:length(ro)) {
        for (v in 1:length(var_error)) {
          for (mt in 1:length(model.type)) {
            eval(parse(text = paste0("result_shared_",name.model[mt]," <- list()")))
            for (j in 2:length(n.save)) {
              eval(parse(text = paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/SCM/",model.type[mt],"/ro_",ro[i],"_sd_",var_error[v],"/",scenarios[s],"_",model.type[mt],"_ro_",ro[i],"_sd_",var_error[v],"_",n.save[j],".RData')")))
              eval(parse(text = paste0("result_shared_",name.model[mt],"[(n.save[j-1]+1):n.save[j]] <- results_shared_",name.model[mt],"[1:20]"))) 
          
            }
            
            eval(parse(text = paste0("results_shared_",name.model[mt]," <- list()")))
            
            eval(parse(text = paste0("save_index <- which(names(result_shared_",name.model[mt],"[[1]])=='dic' |
          names(result_shared_",name.model[mt],"[[1]])=='waic' |
          names(result_shared_",name.model[mt],"[[1]])=='summary.fitted.values' |
          names(result_shared_",name.model[mt],"[[1]])=='marginals.fitted.values')")))
          
            eval(parse(text = paste0("results_shared_",name.model[mt]," <- lapply(1:n.sim, function(x) result_shared_",name.model[mt],"[[x]][save_index])")))
          
            eval(parse(text = paste0("results_shared_",name.model[mt]," <- results_shared_",name.model[mt],"[selec_sim]")))
          
            eval(parse(text = paste0("save(results_shared_",name.model[mt],", file='./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/",model.type[mt],"/ro_",ro[i],"_sd_",var_error[v],"/",scenarios[s],"_",model.type[mt],"_ro_",ro[i],"_sd_",var_error[v],".Rdata')")))
          }
        }
      }
    }
  }
  
  ###Scenario3
  if (scenarios[s]=="S3"){
    #Open selec_sim
    eval(parse(text = paste0("load('./Selected_Simulations/",scenarios[s],"/Selec_sim_",scenarios[s],".Rdata')")))
    for (kp in 1:length(known.per)){
      for (mt in 1:length(model.type)) {
        eval(parse(text = paste0("result_shared_",name.model[mt]," <- list()")))
        for (j in 2:length(n.save)) {
          eval(parse(text = paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/SCM/",model.type[mt],"/",scenarios[s],"_",model.type[mt],"_",n.save[j],".RData')")))
          eval(parse(text = paste0("result_shared_",name.model[mt],"[(n.save[j-1]+1):n.save[j]] <- results_shared_",name.model[mt],"[1:20]")))  
        }
      
        eval(parse(text = paste0("results_shared_",name.model[mt]," <- list()")))
            
        eval(parse(text = paste0("save_index <- which(names(result_shared_",name.model[mt],"[[1]])=='dic' |
          names(result_shared_",name.model[mt],"[[1]])=='waic' |
          names(result_shared_",name.model[mt],"[[1]])=='summary.fitted.values' |
          names(result_shared_",name.model[mt],"[[1]])=='marginals.fitted.values')")))
          
        eval(parse(text = paste0("results_shared_",name.model[mt]," <- lapply(1:n.sim, function(x) result_shared_",name.model[mt],"[[x]][save_index])")))
          
        eval(parse(text = paste0("results_shared_",name.model[mt]," <- results_shared_",name.model[mt],"[selec_sim]")))
          
        eval(parse(text = paste0("save(results_shared_",name.model[mt],", file='./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/",model.type[mt],"/",scenarios[s],"_",model.type[mt],".Rdata')")))
      }
    }
  }
  
  ####Scenario4
  if (scenarios[s]=="S4"){
    #Open selec_sim
    eval(parse(text = paste0("load('./Selected_Simulations/",scenarios[s],"/Selec_sim_",scenarios[s],".Rdata')")))
    for (kp in 1:length(known.per)){
      for (v in 1:length(var_error)) {
        for (mt in 1:length(model.type)) {
          eval(parse(text = paste0("result_shared_",name.model[mt]," <- list()")))
          for (j in 2:length(n.save)) {
          eval(parse(text = paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/SCM/",model.type[mt],"/sd_",var_error[v],"/",scenarios[s],"_",model.type[mt],"_sd_",var_error[v],"_",n.save[j],".RData')")))
            eval(parse(text = paste0("result_shared_",name.model[mt],"[(n.save[j-1]+1):n.save[j]] <- results_shared_",name.model[mt],"[1:20]")))  
        
          }
          
          eval(parse(text = paste0("results_shared_",name.model[mt]," <- list()")))
            
          eval(parse(text = paste0("save_index <- which(names(result_shared_",name.model[mt],"[[1]])=='dic' |
          names(result_shared_",name.model[mt],"[[1]])=='waic' |
          names(result_shared_",name.model[mt],"[[1]])=='summary.fitted.values' |
          names(result_shared_",name.model[mt],"[[1]])=='marginals.fitted.values')")))
          
          eval(parse(text = paste0("results_shared_",name.model[mt]," <- lapply(1:n.sim, function(x) result_shared_",name.model[mt],"[[x]][save_index])")))
          
          eval(parse(text = paste0("results_shared_",name.model[mt]," <- results_shared_",name.model[mt],"[selec_sim]")))
          
          eval(parse(text = paste0("save(results_shared_",name.model[mt],", file='./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/SCM/",model.type[mt],"/sd_",var_error[v],"/",scenarios[s],"_",model.type[mt],"_sd_",var_error[v],".Rdata')")))
        }
      }
    }
  }
}
```

Finally, we save the results of the M-models obtained in the 100 selected simulations and the elements we are interested in.

```{r}
#############################################################################################                            M-Models                           ##########
###################################################################################


for (s in 1:length(scenarios)) {
  for (p in 1:length(priors)) {
    for (d in 1:length(method)) {
      ###Scenario0
      if (scenarios[s]=="S0"){
        #Open selec_sim
        eval(parse(text = paste0("load('./Selected_Simulations/",scenarios[s],"/Selec_sim_",scenarios[s],".Rdata')")))
        for (kp in 1:length(known.per)){
          for (i in 1:length(ro)) {
            eval(parse(text = paste0("result_",priors[p],"_",method[d],"_specI<-list()")))
            for (j in 2:length(n.save)) {
              eval(parse(text= paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/M_Model/ro_",ro[i],"/",scenarios[s],"_",priors[p],"_",method[d],"_ro_",ro[i],"_",n.save[j],".RData')")))
              eval(parse(text = paste0("result_",priors[p],"_",method[d],"_specI[(n.save[j-1]+1):n.save[j]] <- results_",priors[p],"_",method[d],"_specI[1:20]")))
            }
          
            eval(parse(text = paste0("results_",priors[p],"_",method[d],"_specI<-list()")))
          
            eval(parse(text = paste0("save_index <- which(names(result_",priors[p],"_",method[d],"_specI[[1]])=='dic' |
            names(result_",priors[p],"_",method[d],"_specI[[1]])=='waic' |
            names(result_",priors[p],"_",method[d],"_specI[[1]])=='summary.fitted.values' |
            names(result_",priors[p],"_",method[d],"_specI[[1]])=='marginals.fitted.values')")))
          
            eval(parse(text = paste0("results_",priors[p],"_",method[d],"_specI <- lapply(1:n.sim, function(x) result_",priors[p],"_",method[d],"_specI[[x]][save_index])")))
          
            eval(parse(text = paste0("results_",priors[p],"_",method[d],"_specI <- results_",priors[p],"_",method[d],"_specI[selec_sim]")))
          
            eval(parse(text = paste0("save(results_",priors[p],"_",method[d],"_specI, file='./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/ro_",ro[i],"/",scenarios[s],"_",priors[p],"_",method[d],"_ro_",ro[i],".Rdata')")))
          
          }
        }
      }
  
  
      ###Scenario1 and Scenario2
      if (scenarios[s]=="S1" | scenarios[s]=="S2"){
        #Open selec_sim
        eval(parse(text = paste0("load('./Selected_Simulations/",scenarios[s],"/Selec_sim_",scenarios[s],".Rdata')")))
        for (kp in 1:length(known.per)){
          for (i in 1:length(ro)) {
            for (v in 1:length(var_error)) {
              eval(parse(text = paste0("result_",priors[p],"_",method[d],"_specI<-list()")))
              for (j in 2:length(n.save)) {
                eval(parse(text= paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/M_Model/ro_",ro[i],"_sd_",var_error[v],"/",scenarios[s],"_",priors[p],"_",method[d],"_ro_",ro[i],"_sd_",var_error[v],"_",n.save[j],".RData')")))
                eval(parse(text = paste0("result_",priors[p],"_",method[d],"_specI[(n.save[j-1]+1):n.save[j]] <- results_",priors[p],"_",method[d],"_specI[1:20]"))) 
          
              }
            
              eval(parse(text = paste0("results_",priors[p],"_",method[d],"_specI <- list()")))
            
              eval(parse(text = paste0("save_index <- which(names(result_",priors[p],"_",method[d],"_specI[[1]])=='dic' |
          names(result_",priors[p],"_",method[d],"_specI[[1]])=='waic' |
          names(result_",priors[p],"_",method[d],"_specI[[1]])=='summary.fitted.values' |
          names(result_",priors[p],"_",method[d],"_specI[[1]])=='marginals.fitted.values')")))
          
              eval(parse(text = paste0("results_",priors[p],"_",method[d],"_specI <- lapply(1:n.sim, function(x) result_",priors[p],"_",method[d],"_specI[[x]][save_index])")))
          
              eval(parse(text = paste0("results_",priors[p],"_",method[d],"_specI <- results_",priors[p],"_",method[d],"_specI[selec_sim]")))
          
              eval(parse(text = paste0("save(results_",priors[p],"_",method[d],"_specI, file='./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/ro_",ro[i],"_sd_",var_error[v],"/",scenarios[s],"_",priors[p],"_",method[d],"_ro_",ro[i],"_sd_",var_error[v],".Rdata')")))
            }
          }
        }
      }
  
  
      ###Scenario3
      if (scenarios[s]=="S3"){
        #Open selec_sim
        eval(parse(text = paste0("load('./Selected_Simulations/",scenarios[s],"/Selec_sim_",scenarios[s],".Rdata')")))
        for (kp in 1:length(known.per)){
          eval(parse(text = paste0("result_",priors[p],"_",method[d],"_specI<-list()")))
          for (j in 2:length(n.save)) {
            eval(parse(text= paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/M_Model/",scenarios[s],"_",priors[p],"_",method[d],"_",n.save[j],".RData')")))
            eval(parse(text = paste0("result_",priors[p],"_",method[d],"_specI[(n.save[j-1]+1):n.save[j]] <- results_",priors[p],"_",method[d],"_specI[1:20]")))  
          }
        
          eval(parse(text = paste0("results_",priors[p],"_",method[d],"_specI <- list()")))
              
          eval(parse(text = paste0("save_index <- which(names(result_",priors[p],"_",method[d],"_specI[[1]])=='dic' |
            names(result_",priors[p],"_",method[d],"_specI[[1]])=='waic' |
            names(result_",priors[p],"_",method[d],"_specI[[1]])=='summary.fitted.values' |
            names(result_",priors[p],"_",method[d],"_specI[[1]])=='marginals.fitted.values')")))
            
          eval(parse(text = paste0("results_",priors[p],"_",method[d],"_specI <- lapply(1:n.sim, function(x) result_",priors[p],"_",method[d],"_specI[[x]][save_index])")))
            
          eval(parse(text = paste0("results_",priors[p],"_",method[d],"_specI <- results_",priors[p],"_",method[d],"_specI[selec_sim]")))
            
          eval(parse(text = paste0("save(results_",priors[p],"_",method[d],"_specI, file='./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/",scenarios[s],"_",priors[p],"_",method[d],".Rdata')")))
        }
      }
  
  
      ####Scenario4
      if (scenarios[s]=="S4"){
        #Open selec_sim
        eval(parse(text = paste0("load('./Selected_Simulations/",scenarios[s],"/Selec_sim_",scenarios[s],".Rdata')")))
        for (kp in 1:length(known.per)){
          for (v in 1:length(var_error)) {
            eval(parse(text = paste0("result_",priors[p],"_",method[d],"_specI<-list()")))
            for (j in 2:length(n.save)) {
              eval(parse(text= paste0("load('./",scenarios[s],"/Cov_",known.per[kp],"/M_Model/sd_",var_error[v],"/",scenarios[s],"_",priors[p],"_",method[d],"_sd_",var_error[v],"_",n.save[j],".RData')")))
              eval(parse(text = paste0("result_",priors[p],"_",method[d],"_specI[(n.save[j-1]+1):n.save[j]] <- results_",priors[p],"_",method[d],"_specI[1:20]")))  
        
            }
          
            eval(parse(text = paste0("results_",priors[p],"_",method[d],"_specI <- list()")))
            
            eval(parse(text = paste0("save_index <- which(names(result_",priors[p],"_",method[d],"_specI[[1]])=='dic' |
          names(result_",priors[p],"_",method[d],"_specI[[1]])=='waic' |
          names(result_",priors[p],"_",method[d],"_specI[[1]])=='summary.fitted.values' |
          names(result_",priors[p],"_",method[d],"_specI[[1]])=='marginals.fitted.values')")))
          
            eval(parse(text = paste0("results_",priors[p],"_",method[d],"_specI <- lapply(1:n.sim, function(x) result_",priors[p],"_",method[d],"_specI[[x]][save_index])")))
          
            eval(parse(text = paste0("results_",priors[p],"_",method[d],"_specI <- results_",priors[p],"_",method[d],"_specI[selec_sim]")))
          
            eval(parse(text = paste0("save(results_",priors[p],"_",method[d],"_specI, file='./Selected_Simulations/",scenarios[s],"/Cov_",known.per[kp],"/M_Model/sd_",var_error[v],"/",scenarios[s],"_",priors[p],"_",method[d],"_sd_",var_error[v],".Rdata')")))
          }
        }
      }
    }
  }
}
```
